High-Performance Language Primitives for Distributed Architectures using Asynchronous Events

### 2012-07-23 doc/asplos2013/results.tex
section 5 edits

In this section we demonstrate the performance properties of three
real-world applications that use the Legion runtime and by extension the heterogeneous
implementation of our interface to run on the Keeneland supercomputer.
The three applications that we characterize are all multi-phase
applications that require parallel computation, data exchange, and
synchronization between phases.

@@

In Section~\ref{subsec:eventlife} we study the lifetime of events in
the Fluid application.  Section~\ref{subsec:lockmig} examines
the migration of locks in the Circuit application.  Finally, we demonstrate
that the asynchronous nature of our interface is essential to the
performance of Legion by comparing to bulk-synchronous
implementations of our target applications in Section~\ref{subsec:bulkcomp}.

@@

Our last set of experiments demonstrates that the asynchronous nature of our interface
is essential to the high performance of the Legion runtime system.  The Legion
implementations of our three applications have already been shown to outperform 
pre-existing implementations\cite{Legion12}.  To quantify the benefit of the asynchronous
nature of our interface, we implemented versions of our applications in
Legion in a bulk-synchronous style to compare against our existing implementations.  
These bulk-synchronous versions still run on top of 
the Legion runtime, but invoke blocking operations between computational phases,
communication phases, and synchronization.

Figure~\ref{fig:bulksync} compares
the performance of the bulk-synchronous implementations versus the original
implementations for Circuit, Fluid, and AMR respectively.  Each plot contains
performance curves for both implementations on two different problem sizes.
Circuit is a compute-bound application and the bulk-synchronous implementation
performs reasonably well.  By 16 nodes however the overhead grows to 19\%
and 22\% on the small and large inputs respectively.  The Fluid application 
has a more evenly balanced computation-to-communication ratio.  As a result,
Fluid performance suffers significantly more by switching to
a bulk-synchronous model.  At 16 nodes, performance is 135\% and 52\% worse
than the original Legion implementations on the small and large problem sizes
respectively.  Finally, the AMR application is a memory bound application, and on 16 nodes
the bulk-synchronous version is 82\% and 102\% slower on the small and
large problem sizes.

>>>>

In this section we demonstrate the performance properties of three
real-world applications that use the Legion runtime and the heterogeneous
implementation of our interface to run on the Keeneland supercomputer.
The three applications that we characterize are all multi-phase
applications that require parallel computation, data exchange, and
synchronization between phases.

@@

In Section~\ref{subsec:eventlife} we study the lifetime of events in
the Fluid application.  Section~\ref{subsec:lockmig} examines
the migration of locks in the Circuit and AMR applications.  Finally, we demonstrate
that the asynchronous nature of our interface is essential to the
performance of Legion by comparing to bulk-synchronous
implementations of these applications in Section~\ref{subsec:bulkcomp}.

@@

Our last set of experiments demonstrates that the asynchronous nature of our interface
is essential to the high performance of the Legion runtime system.  The Legion
implementations of the three applications have already been shown to outperform 
pre-existing implementations\cite{Legion12}.  To quantify the benefit of the asynchronous
nature of our interface, we re-implemented the applications in
a bulk-synchronous style to compare against the existing Legion implementations.  
These bulk-synchronous versions still run on top of 
the Legion runtime, but invoke blocking operations between computational phases,
communication phases, and synchronization.

Figure~\ref{fig:bulksync} compares
the performance of the bulk-synchronous implementations versus the original
implementations for Circuit, Fluid, and AMR.  Each plot contains
performance curves for both implementations on two different problem sizes.
Circuit is a compute-bound application and the bulk-synchronous implementation
performs reasonably well.  By 16 nodes however the overhead grows to 19\%
and 22\% on the small and large inputs respectively.  The Fluid application 
has a more evenly balanced computation-to-communication ratio.  As a result,
Fluid performance suffers significantly more by switching to
a bulk-synchronous model.  At 16 nodes, performance is 135\% and 52\% worse
than the original Legion implementations on the small and large problem sizes
respectively.  Finally, the AMR application is a memory bound application, and on 16 nodes
the bulk-synchronous version is 82\% and 102\% slower on the small and
large problem sizes.
